\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{array}

\title{Software Design Document}
\author{Group 5: Gabe Foreman, Lester Low, Jose Oscanoa, Christine Vu}
\date{November 21, 2024}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Version Description}
\begin{table}[h!]
    \centering
    \begin{tabular}{c|c|c}
    \hline
    Version Number & Description & Date Added \\ \hline
    Data 1 & Date 2 & Data 3 \\ \hline
    Data 4 & Date 5 & Data 6 \\ \hline
    \end{tabular}
    \label{tab:my_label}
\end{table}

\section{Sections}
\subsection{Introduction}
\begin{itemize}
    \item \textbf{Purpose of the Document}         
            
            The purpose of this document is to outline the requirements for the final project. It serves as a reference for the team.
            
    \item \textbf{Intended Audience} 
            
            This document is intended for software developers.
            
    \item \textbf{Overview of the Software}
            
            This project is a web and mobile application that allows anyone to post fun and interesting events or stories.

\end{itemize}

\subsection{System Architecture}
\begin{itemize}
    \item \textbf{User Interface:}

            The system consists of several components working together to achieve its functionality. The user interacts with the front-end interface, which communicates with the back-end server to process and store data. 

    \item \textbf{Software Interfaces:}
        \begin{itemize}
            \item \textbf{Client-side}: The client-side includes the web and mobile application interfaces, where users can upload and interact with content.
            \item \textbf{Server-side}: The server processes requests, handles user authentication, and stores content in the database.
            \item \textbf{Database}: The database stores user data, posts, and other relevant information, ensuring quick access and retrieval.
        \end{itemize}

\end{itemize}

\subsection{User Interface}
\begin{itemize}
    \item \textbf{How to Use the System}
        
            Users can create an account, post content, interact with other posts, and manage their personal settings.
        
    \item \textbf{Database Design and Explanation}
        
            The database is structured into tables for users, posts, comments, and likes. The relationships between these tables allow for efficient querying and data retrieval.
        
\end{itemize}

\subsection{Glossary}
\begin{tabular}{|c|c|}
    \hline
    \textbf{Acronym/Term} & \textbf{Definition} \\
    \hline
    UI & User Interface \\
    API & Application Programming Interface \\
    GDPR & General Data Protection Regulation \\
    \hline
\end{tabular}
    
\end{document}
